To Airbnb?: A Question of Returns

### 2017-10-25 abb_Writeup.Rmd
Initial Update for ARES 2018
Update to Writeup for ARES 2018

---
title: "Should I Airbnb My Property?"
author: "Andy Krause and Gideon Aschwanden"
date: "March 17, 2017"
output:
  pdf_document: default
  html_document: default
header-includes: 
   - \usepackage{setspace}\doublespacing
   - \usepackage{caption}
   - \captionsetup[table]{skip=10pt}
geometry: margin=3.3cm
bibliography: abb.bib
---

@@

  # Get computer names

  comp.name <- Sys.info()['nodename']

  # Assign path based on computer name

  if(comp.name == '7020D-121777-W' | comp.name == 'DESKTOP-1D7JO4J'){

@@

  } else {

    data.path <- 'alternate data path'
    code.path <- 'alternate code path'
    fig.path <- 'alternate fig path'

  }

@@

  source(paste0(code.path, "dataviztools/ggplottools.R"))
  source(paste0(code.path, "datamgmttools/dataMungetools.R"))
  source(paste0(code.path, "research/AirbnbMelbourne/abb_Functions.R"))

@@

  abb.col[1] <- abb.col[3]
  abb.col[5] <- abb.col[6]

@@

   load(paste0(data.path, '/analyzed/analyzed_workspace.RData'))
   a<-1

@@

  rate.hm <- abbHeatMap(str.data.ic,
                x.field='occ.rate',
                y.field='med.rate',
                pref.field='str.act.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))
  rate.hm <- rate.hm + ylab('Nightly Rate')

@@

  rate.hm.svm <- abbHeatMap(str.data.ic,
                            x.field='occ.rate',
                            y.field='med.rate',
                            pref.field='str.act.pref',
                            svm=T, 
                            alpha.count=F,
                            add.points=T,
                            fill.colors=c(abb.col[1], abb.col[5]))
  rate.hm.svm <- rate.hm.svm + ylab('Nightly Rate')

@@

  qtl.hm <- abbHeatMap(str.data.ic,
                x.field='occ.qtl',
                y.field='rate.qtl',
                pref.field='str.act.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))
  qtl.hm <- qtl.hm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)')

@@

  qtl.hm.svm <- abbHeatMap(str.data.ic,
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T, 
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))
  qtl.hm.svm <- qtl.hm.svm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)')

@@

  house.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
                                          'House', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5])) +
  theme(legend.position='none') +
  annotate("text", x = 50, y = 50, label = "Houses", size=9) +
  ylab('Nightly Rate (Pcntl)') +
  xlab('Occupancy Rate (Pcntl)')

@@

  apt.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
                                          'Apartment', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))+
  theme(legend.position='none')+
  annotate("text", x = 50, y = 50, label = "Apartments", size=9)+
  ylab('Nightly Rate (Pcntl)') +
  xlab('Occupancy Rate (Pcntl)')

@@

 # Make Basic comparison table
  pref.table <- abbCreateCompTable(ic.df=str.data.ic,
                                   split.field='geo.mrkt')

@@

  core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                          'city-core', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5])) +
  theme(legend.position='none') +
    ylab('Nightly Rate Percentile') +
    xlab('Occupancy Rate Percentile') +
  annotate("text", x = 50, y = 50, label = "City-Core", size=9)

  city.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                          'city', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))+
  theme(legend.position='none')+
    ylab('Nightly Rate Percentile') +
    xlab('Occupancy Rate Percentile') +
  annotate("text", x = 50, y = 50, label = "City", size=9)

  sub.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                          'suburban', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))+
  theme(legend.position='none')+
    ylab('Nightly Rate Percentile') +
    xlab('Occupancy Rate Percentile') +
  annotate("text", x = 50, y = 50, label = "Suburban", size=9)

  rural.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                          'rural', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))+
  theme(legend.position='none')+
    ylab('Nightly Rate Percentile') +
    xlab('Occupancy Rate Percentile') +
  annotate("text", x = 50, y = 50, label = "Rural", size=9)

  beach.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                          'beach', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))+
  theme(legend.position='none')+
    ylab('Nightly Rate Percentile') +
    xlab('Occupancy Rate Percentile') +
  annotate("text", x = 50, y = 50, label = "Beach", size=9)

@@

  # Extract diagnostics
  str.dx <- logDx(pref.models[[1]], str.data.ic, str.data.ic$str.act.pref)
  sm.dx <- logDx(pref.models[[2]], str.data.ic, str.data.ic$str.act.pref)
  host.dx <- logDx(pref.models[[3]], str.data.ic, str.data.ic$str.act.pref)

@@

 # Make Basic comparison table of type
  tpref.table <- abbCreateCompTable(ic.df=str.data.ic,
                                    split.field='type')
 # Extract Potential Results
  tpref.table <- tpref.table[tpref.table$rev.type == 'Potential', ]

 # Make baseic comparison table of submarkets  
  spref.table <- abbCreateCompTable(ic.df=str.data.ic,
                                    split.field='geo.mrkt')

@@

  pqtl.hm <- abbHeatMap(pot.data.ic,
                x.field='occ.qtl',
                y.field='rate.qtl',
                pref.field='str.pot.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))
  pqtl.hm <- pqtl.hm + ylab('Nightly Rate (Qtl)')

@@

  pqtl.hm.svm <- abbHeatMap(pot.data.ic,
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.pot.pref',
                   svm=T, 
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))
  pqtl.hm.svm <- pqtl.hm.svm + ylab('Nightly Rate (Pcntl)')+
    xlab('Occupancy Rate (Pcntl)') +
  annotate("text", x = 50, y = 50, label = "Potential", size=9)

@@

  # Extract diagnostics
  pstr.dx <- logDx(pref.models[[4]], str.data.ic, str.data.ic$str.pot.pref)
  psm.dx <- logDx(pref.models[[5]], str.data.ic, str.data.ic$str.pot.pref)
  phost.dx <- logDx(pref.models[[6]], str.data.ic, str.data.ic$str.pot.pref)

@@

  host.block.freq <- ggplot(str.data, aes(x=block.rate)) + 
  geom_density(fill=str.col, color=str.col) +
  ylab('Frequency\n') + 
  xlab('\n% of Time Property is Blocked') +
  scale_x_continuous(breaks=seq(0,1,.2),
                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    #ggtitle('Host Block Rate Frequency\n') +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme(axis.text.y=element_blank(),
          axis.ticks.y=element_blank())
```

@@

  block.rate.period <- ggplot(str.data, aes(x=block.rate, y=nbr.block*extr.par)) + 
  geom_point(fill=str.col, color=str.col, size=.2) +
  ylab('Nbr of Blocked Periods\n') + 
  xlab('\n% of Time Property is Blocked') +
  scale_x_continuous(breaks=seq(0, 1, .2),
                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    #ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  str.data$blockpertime <- round(str.data$nbr.block * str.data$extr.par, 1)

  str.data$host.type <- 'Unknown'
  str.data$host.type[str.data$blockpertime > 12] <- 'Multi-Platform User'
  str.data$host.type[str.data$block.rate <= .25] <- 'Profit Seeker'
  str.data$host.type[str.data$block.rate >= .75] <- 'Opportunistic Sharer'
  str.data$host.type <- factor(str.data$host.type,
                               levels=c('Profit Seeker', 'Opportunistic Sharer', 
                                        'Multi-Platform User', 'Unknown'))
```

@@

  base.host <- ggplot(str.data, 
                    aes(x=block.rate, y=blockpertime)) + 
                geom_point(alpha=.7, size=.4, shape=16, color='gray70') +
                ylab('# Blckd Periods\n') + 
                xlab('\n% of Time Property is Blocked') +
                ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
                scale_x_continuous(breaks=seq(0, 1, .2),
                                   labels=c('0%', '20%', '40%', 
                                            '60%', '80%', '100%')) +
                #scale_color_manual(values=c(abb.col[2], abb.col[4], 
                #                            abb.col[7], abb.col[9])) + 
                theme(legend.position='bottom',
                      legend.title = element_blank(),
                      plot.title = element_text(hjust = 0.5))+
                guides(colour = guide_legend(override.aes = list(size=3,                                                                       alpha=1)))

@@

  ps.host <- base.host + 
    geom_point(data=str.data[str.data$host.type == 'Profit Seeker', ], size=.4)  +
    ggtitle('Profit Seekers')

  os.host <- base.host + 
    geom_point(data=str.data[str.data$host.type == 'Opportunistic Sharer', ], 
               size=.4)  +
    ggtitle('Opportunistic Sharer')

  mu.host <- base.host + 
    geom_point(data=str.data[str.data$host.type == 'Multi-Platform User', ], 
               size=.4)  +
    ggtitle('Multi-Platform User')

  un.host <- base.host + 
    geom_point(data=str.data[str.data$host.type == 'Unknown', ], size=.4)  +
    ggtitle('Unknown')

@@

  host.type.bar <- ggplot(str.data, aes(host.type, fill=host.type)) +
    geom_bar() +
    scale_fill_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9]))+
    theme(legend.position='none') +
    ylab('Frequency\n') + 
    xlab('\nHost Type') +
    scale_x_discrete(labels=c('Profit','Sharer','Multi','Unk'))+
    #ggtitle('short-term Host Types') + 
    theme(plot.title = element_text(hjust = 0.5))

@@

 # Make Basic comparison table
  apref.table <- abbCreateCompTable(ic.df=str.data.ic,
                                    split.field='host.type')

@@

  # Extract diagnostics
  hstr.dx <- logDx(host.models[[1]], str.data.ic, str.data.ic$str.act.pref)
  hsm.dx <- logDx(host.models[[3]], str.data.ic, str.data.ic$str.act.pref)
  hhost.dx <- logDx(host.models[[4]], str.data.ic, str.data.ic$str.act.pref)

>>>>

---
title: "To Airbnb?: A Question of Returns"
subtitle: "Andy Krause and Gideon Aschwanden"
author: "Greenfield Advisors and University of Melbourne"
date: "October 25th, 2017"
output:
  pdf_document: default
  html_document: default
header-includes: 
   - \usepackage{setspace}\doublespacing
   - \usepackage{caption}
   - \captionsetup[table]{skip=10pt}
geometry: margin=3.3cm
bibliography: abb.bib
---

@@

@@

@@

  source(paste0(code.path, "tools/dataviztools/ggplottools.R"))
  source(paste0(code.path, "tools/datamgmttools/dataMungetools.R"))
  source(paste0(code.path, "research/AirbnbMelbourne/abb_Functions.R"))

@@

  strp.col <- abb.col[3]
  ltrp.col <- abb.col[6]

@@

   load(paste0(data.path, '/analyzed/analyzed_workspace_sep.RData'))
   a<-1

@@

  rate.hm <- abbHeatMap(str_df.ic,
                x.field='occ.rate',
                y.field='med.rate',
                pref.field='str.act.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(strp.col, ltrp.col))
  rate.hm <- rate.hm + ylab('Nightly Rate')

@@

  rate.hm.svm <- abbHeatMap(str_df.ic,
                            x.field='occ.rate',
                            y.field='med.rate',
                            pref.field='str.act.pref',
                            svm=T, 
                            alpha.count=F,
                            add.points=T,
                            fill.colors=c(strp.col, ltrp.col))
  rate.hm.svm <- rate.hm.svm + ylab('Nightly Rate')

@@

  qtl.hm <- abbHeatMap(str_df.ic,
                x.field='occ.qtl',
                y.field='rate.qtl',
                pref.field='str.act.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(strp.col, ltrp.col))
  qtl.hm <- qtl.hm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)')

@@

  qtl.hm.svm <- abbHeatMap(str_df.ic,
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T, 
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(strp.col, ltrp.col))
  qtl.hm.svm <- qtl.hm.svm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)')

@@

  house.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
                                          'House', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(strp.col, ltrp.col)) +
  theme(legend.position='none') +
  annotate("text", x = 50, y = 50, label = "Houses", size=9) +
  ylab('Nightly Rate (Pcntl)') +
  xlab('Occupancy Rate (Pcntl)')

@@

  apt.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
                                          'Apartment', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(strp.col, ltrp.col))+
  theme(legend.position='none')+
  annotate("text", x = 50, y = 50, label = "Apartments", size=9)+
  ylab('Nightly Rate (Pcntl)') +
  xlab('Occupancy Rate (Pcntl)')

@@

 # Make Basic comparison table
  pref.table <- abbCreateCompTable(ic.df=str_df.ic,
                                   split.field='geo.mrkt')

@@

  core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                          'city-core', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(strp.col, ltrp.col)) +
  theme(legend.position='none') +
    ylab('Nightly Rate Percentile') +
    xlab('Occupancy Rate Percentile') +
  annotate("text", x = 50, y = 50, label = "City-Core", size=9)

  city.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                          'city', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(strp.col, ltrp.col))+
  theme(legend.position='none')+
    ylab('Nightly Rate Percentile') +
    xlab('Occupancy Rate Percentile') +
  annotate("text", x = 50, y = 50, label = "City", size=9)

  sub.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                          'suburban', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(strp.col, ltrp.col))+
  theme(legend.position='none')+
    ylab('Nightly Rate Percentile') +
    xlab('Occupancy Rate Percentile') +
  annotate("text", x = 50, y = 50, label = "Suburban", size=9)

  rural.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                          'rural', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(strp.col, ltrp.col))+
  theme(legend.position='none')+
    ylab('Nightly Rate Percentile') +
    xlab('Occupancy Rate Percentile') +
  annotate("text", x = 50, y = 50, label = "Rural", size=9)

  beach.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                          'beach', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(strp.col, ltrp.col))+
  theme(legend.position='none')+
    ylab('Nightly Rate Percentile') +
    xlab('Occupancy Rate Percentile') +
  annotate("text", x = 50, y = 50, label = "Beach", size=9)

@@

  # Extract diagnostics
  str.dx <- logDx(pref.models[[1]], str_df.ic, str_df.ic$str.act.pref)
  sm.dx <- logDx(pref.models[[2]], str_df.ic, str_df.ic$str.act.pref)
  host.dx <- logDx(pref.models[[3]], str_df.ic, str_df.ic$str.act.pref)

@@

 # Make Basic comparison table of type
  tpref.table <- abbCreateCompTable(ic.df=str_df.ic,
                                    split.field='type')
 # Extract Potential Results
  tpref.table <- tpref.table[tpref.table$rev.type == 'Potential', ]

 # Make baseic comparison table of submarkets  
  spref.table <- abbCreateCompTable(ic.df=str_df.ic,
                                    split.field='geo.mrkt')

@@

  pqtl.hm <- abbHeatMap(pot.data.ic,
                x.field='occ.qtl',
                y.field='rate.qtl',
                pref.field='str.pot.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(strp.col, ltrp.col))
  pqtl.hm <- pqtl.hm + ylab('Nightly Rate (Qtl)')

@@

  pqtl.hm.svm <- abbHeatMap(pot.data.ic,
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.pot.pref',
                   svm=T, 
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(strp.col, ltrp.col))
  pqtl.hm.svm <- pqtl.hm.svm + ylab('Nightly Rate (Pcntl)')+
    xlab('Occupancy Rate (Pcntl)') +
  annotate("text", x = 50, y = 50, label = "Potential", size=9)

@@

  # Extract diagnostics
  pstr.dx <- logDx(pref.models[[4]], str_df.ic, str_df.ic$str.pot.pref)
  psm.dx <- logDx(pref.models[[5]], str_df.ic, str_df.ic$str.pot.pref)
  phost.dx <- logDx(pref.models[[6]], str_df.ic, str_df.ic$str.pot.pref)

@@

  host.block.freq <- ggplot(str_df, aes(x=block.rate)) + 
  geom_density(fill=str.col, color=str.col) +
  ylab('Frequency\n') + 
  xlab('\n% of Time Property is Blocked') +
  scale_x_continuous(breaks=seq(0,1,.2),
                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    #ggtitle('Host Block Rate Frequency\n') +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme(axis.text.y=element_blank(),
          axis.ticks.y=element_blank())
```

@@

  block.rate.period <- ggplot(str_df, aes(x=block.rate, y=nbr.block*extr.par)) + 
  geom_point(fill=str.col, color=str.col, size=.2) +
  ylab('Nbr of Blocked Periods\n') + 
  xlab('\n% of Time Property is Blocked') +
  scale_x_continuous(breaks=seq(0, 1, .2),
                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    #ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  str_df$blockpertime <- round(str_df$nbr.block * str_df$extr.par, 1)

  str_df$host.type <- 'Unknown'
  str_df$host.type[str_df$blockpertime > 12] <- 'Multi-Platform User'
  str_df$host.type[str_df$block.rate <= .25] <- 'Profit Seeker'
  str_df$host.type[str_df$block.rate >= .75] <- 'Opportunistic Sharer'
  str_df$host.type <- factor(str_df$host.type,
                               levels=c('Profit Seeker', 'Opportunistic Sharer', 
                                        'Multi-Platform User', 'Unknown'))
```

@@

  base.host <- ggplot(str_df, 
                    aes(x=block.rate, y=blockpertime)) + 
                geom_point(alpha=.7, size=.4, shape=16, color='gray70') +
                ylab('# Blckd Periods\n') + 
                xlab('\n% of Time Property is Blocked') +
                ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
                scale_x_continuous(breaks=seq(0, 1, .2),
                                   labels=c('0%', '20%', '40%', 
                                            '60%', '80%', '100%')) +
                #scale_color_manual(values=c(abb.col[2], abb.col[4], 
                #                            abb.col[7], abb.col[9])) + 
                theme(legend.position='bottom',
                      legend.title = element_blank(),
                      plot.title = element_text(hjust = 0.5))+
                guides(colour = guide_legend(override.aes = list(size=3,                                                                       alpha=1)))

@@

  ps.host <- base.host + 
    geom_point(data=str_df[str_df$host.type == 'Profit Seeker', ], size=.4)  +
    ggtitle('Profit Seekers')

  os.host <- base.host + 
    geom_point(data=str_df[str_df$host.type == 'Opportunistic Sharer', ], 
               size=.4)  +
    ggtitle('Opportunistic Sharer')

  mu.host <- base.host + 
    geom_point(data=str_df[str_df$host.type == 'Multi-Platform User', ], 
               size=.4)  +
    ggtitle('Multi-Platform User')

  un.host <- base.host + 
    geom_point(data=str_df[str_df$host.type == 'Unknown', ], size=.4)  +
    ggtitle('Unknown')

@@

  host.type.bar <- ggplot(str_df, aes(host.type, fill=host.type)) +
    geom_bar() +
    scale_fill_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9]))+
    theme(legend.position='none') +
    ylab('Frequency\n') + 
    xlab('\nHost Type') +
    scale_x_discrete(labels=c('Profit','Sharer','Multi','Unk'))+
    #ggtitle('short-term Host Types') + 
    theme(plot.title = element_text(hjust = 0.5))

@@

 # Make Basic comparison table
  apref.table <- abbCreateCompTable(ic.df=str_df.ic,
                                    split.field='host.type')

@@

  # Extract diagnostics
  hstr.dx <- logDx(host.models[[1]], str_df.ic, str_df.ic$str.act.pref)
  hsm.dx <- logDx(host.models[[3]], str_df.ic, str_df.ic$str.act.pref)
  hhost.dx <- logDx(host.models[[4]], str_df.ic, str_df.ic$str.act.pref)
